DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-11-22 2015CompleteDerivation/completeDerivation.tex
More work on the quantum part

	We claim $\bar{\mathcal{S}}$ is the level set for $\mathcal{H} = 0$. $\mathcal{H} = \lambda (H - E) = 0$ over $\bar{\mathcal{S}}$. We can extend $\mathcal{H}$ over $T^* \mathcal{M}$ such that $\mathcal{H} \neq 0$ over $T^*\mathcal{M} \,\backslash\, \bar{\mathcal{S}}$. $\bar{\mathcal{S}}$ is the level set for $\mathcal{H} = 0$
\end{justification}

@@

	We claim the set of physically distinguishable transformations $T$ that change the unstated part of an irreducible material is isomorphic to $\mathbbm{C}$. Consider an amount $a_m \in \mathbbm{R}$ of irreducible material characterized by one d.o.f. The configuration of a fragment is characterized by two random variables $A, B: \Omega \rightarrow \mathbbm{R}$ where $\Omega$ is the sample space for the configuration of the fragments. As the configuration of each fragment is physically indistinguishable, $A$ and $B$ can be chosen such that the distribution $\rho$ of material over such variables is uniform and unitary. We can also rescale $A$ and $B$ such that they are defined on the range $[0, \sqrt{a_m}]$. We have $a_m=\int \rho dA \wedge dB = \int dA \wedge dB$. Consider a second amount $\hat{a}_m$ of irreducible material in the same configuration. It also can be characterized by a uniform distribution over two variables $C, D: \Omega \rightarrow \mathbbm{R}$ over a range of $\sqrt{\hat{a}_m}$. As the two amounts of material are in the same configuration we have $(C,D)$ is a function of $(A,B)$. We have $\hat{a}_m = \int dC \wedge dD = \int |J| dA \wedge dB$ where $|J|$ is the Jacobian determinant. As both distributions are uniform, $|J|$ has to be constant. The transformation has to be linear: $C=aA + bB$ and $D=-bA + aB$. As the amount of material is the only physically distinguishable quantity and is fully specified by $a$ and $b$, no other transformation is physically relevant. Let $\tau: \mathbbm{C} \rightarrow T$ represent such a transformation parametrized by $c=a+\imath b$. $|c|^2 = (a^2 + b^2) = \hat{a}_m / a_m$ is physically distinguishable. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{C}$, so that the sum and product of the transformation is equal to the sum and product of their respective factors. The phase $arg(c)$ under addition is physically distinguishable as it can affect the modulus of the result. $\tau$ is an isomorphism between $T$ and $\mathbbm{C}$ as fields. Generalizing to multiple independent d.o.f. the set of transformation remains the same. The transformation on each d.o.f. is similarly defined by $c_i \in \mathbbm{C}$. As $\hat{a}_m / a_m$ is the same under all d.o.f. $|c_i|=|c_j|$. That has to always hold under addition as well, therefore $arg(c_i) = arg(c_j)$. $T\cong \mathbbm{C}$ even in multiple d.o.f.

	We claim $\Psi$ is a vector space over $\mathbbm{C}$. The abelian group $\Psi$ can be extended with the operations defined by $T$ as done in \ref{classical_vector space} for the infinitesimally reducible case.

@@

If $\mathcal{Q}$ is the space that defines our units, a state $\psi$ must tell us for each point $\mathcal{q} \in \mathcal{Q}$ how much material is there and the the correlation of the unstated part. That is: the state will be identified by $\psi : \mathcal{Q} \rightarrow \mathbbm{C}$, a complex function over the $\mathcal{Q}$.

The square modulus at each point will give us the density of the material. As in the classical case, such density mush be integrable to give us the total amount of material. Therefore the function $\psi \in L^2(\mathcal{Q}, \mu)$ is square integrable. The norm $|\psi|^2 = \int_{\mathcal{Q}} |\psi(q)|^2 dq$ will give us the amount of material associated with the state.

As the material is homogeneous, all particles of the material are made of the same amount. We can set, by convention, the amount of material for a particle to be unitary, therefore quantum particle states are the subset of $\Psi$ such that $|\psi|^2 = 1$. Note that changing the phase by the same amount everywhere is only changes the unstated part. Such change does not change the state, therefore distribution whose differ by a total phase are not physically distinguishable and represent the same physical state.

@@

	We claim $\Psi \cong \Psi(\mathcal{Q}, dp^i) \subseteq C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$ as a vector space. The maximal physical description of a set of fragments is given by a point in $\mathcal{Q}$ parametrized by $q^i$ and by a transformation in $T$ parametrized by $c \in \mathbbm{C}$. For each $\psi \in \Psi$ there must exist a wave function $\psi(q^i) : \mathcal{Q} \rightarrow \mathbbm{C}$ that provides the maximal physical description for the fragments. $\rho_\psi(q^i) = |\psi(q^i)|^2$ as the modulus of $\psi(q^i)$ is the increase/decrease from the unit amount of material. $\rho_\psi(q^i) \in C(\mathcal{Q}, \mathbbm{R})$ by \ref{continuous_map}. Therefore $\psi(q^i) \in C(\mathcal{Q}, \mathbbm{R})$. $\rho_\psi(q^i) \in L^1(\mathcal{Q}, \mu, \mathbbm{R})$ by the same arguments in the justification for \ref{integration}. Therefore $\psi(q^i) \in L^2(\mathcal{Q}, \mu, \mathbbm{C})$. Let $\Upsilon_{q^i} : \Psi \rightarrow C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$ be the function that given a state returns its wave function. As the wave function capture the maximal description of the system, two states must represent different distributions. $\forall \psi_1, \psi_2 \in \Psi, \psi_1 \neq \psi_2 \implies \Upsilon_{q^i}(\psi_1) \neq \Upsilon_{q^i}(\psi_2)$. $\Upsilon_{q^i}$ is injective. $\Upsilon_{q^i}$ is a bijection between $\Psi$ and $\Psi(\mathcal{Q}, dp^i)\equiv\Upsilon_{q^i}(\Psi)$. Let $\psi=\psi_1+\psi_2$, then $\Upsilon_{q^i}(\psi)=\Upsilon_{q^i}(\psi_1)+\Upsilon_{q^i}(\psi_2)$ as combining the distributions means combining the statistical description of the fragments. Let $\psi_1=\tau(c)\psi_2$, then $\Upsilon_{q^i}(\psi_1)=c \Upsilon_{q^i}(\psi_2))$ as $\tau(c)$ transforms the fragment configuration by the factor $C$. $\Upsilon_{q^i}$ is a homomorphism as a vector space. $\Psi$ is isomorphic to $\Psi(\mathcal{Q}, dp^i) \subseteq C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$.

	We claim the state space for a quantum particle is isomorphic to the projective space $\mathsf{P}(\Psi)$. Let $\psi \in \Psi$ be the state of a quantum particle. $e^{\imath \theta} \psi$ with $\theta \in \mathbbm{R}$ is not physically distinguishable from $\psi$ as phases are only physically distinguishable through addition. $\sqrt{\rho} \psi$ with $\sqrt{\rho} \in \mathbbm{R}^+$ cannot represent a quantum particle as it as a different amount of material. There exists only one distinguishable state for a quantum particle in the equivalence class $\psi \sim c \psi$ with $c \in \mathbbm{C}$. The state with no amount of material does not correspond to any particle state. The quotient space $\mathsf{P}(\Psi) \equiv (\Psi - \{0\}) / \sim$ is isomorphic to the state of quantum particles.
\end{justification}

@@

Both in the classical and quantum state the full state is identified by distributions on $\mathcal{Q}$. The $q^i$ do not label the states, but the infinitesimal parts. For a classical material, the infinitesimal parts can be given a state, have their own topological space and a set of local state variables $(q^i, p_i)$ to identify them. We can use the richness of theory of differentiable manifolds and metric spaces. For an irreducible material, the infinitesimal parts cannot be given a state, cannot be identified by a set of local variables. We have to develop other mathematical tools.

To be on par with classical mechanics we need at least address three problems. We need to be able to compare two quantum states and ask what fraction of them share the same configuration: this will give us an inner product. We need to be able to express state variable distributions and expectations: this will give us linear operators. We need to identify the conjugate quantities $k_i$ and $p_i$. Let's start with the first.

The idea is that, given two states $\psi_1$ and $\psi_2$, we should be able to tell how much of $\psi_1$ is prepared in the same way of $\psi_2$. That is $\psi_1 = \alpha \psi_2 + \psi_3$ is the combination of the part that is prepared like $\psi_2$ (e.g. same distributions in position and momentum) and a part that is prepared completely differently. Let $\mathsf{P}_{\psi_2} : \Psi \rightarrow \Psi$ be the operator that gives us the equally prepared part $\mathsf{P}_{\psi_2} (\psi_1) \equiv \alpha \psi_2$. This operator must be linear in $\psi_1$: combining parts that are equally prepared still gives us parts that are equally prepared. It also gives us the same result if applied once or twice: once we isolated the part that is equally prepared, it remains the part that is equally prepared. $\mathsf{P}_{\psi_2}$ is therefore a projection: a linear operator such that $\mathsf{P}^2_{\psi_2}= \mathsf{P}_{\psi_2}$.

This projection has other useful properties. If $\psi_1$ is already prepared like $\psi_2$, then its projection on $\psi_2$ will be equal to $\psi_1$. Conversely, if the projection of $\psi_1$ is equal to itself, then it means that the state is already prepared like $\psi_2$. That is: $\mathsf{P}_{\psi_2} (\psi_1) = \psi_1 \Leftrightarrow \psi_1 = \alpha \psi_2$. Moreover, because the material is irreducible, if $23\%$ of $\psi_1$ is prepared like $\psi_2$, then $23\%$ of $\psi_2$ is prepared like $\psi_1$. If not, we could learn more (or less) about $\psi_1$ by studying the part of $\psi_2$ that is prepared like $\psi_1$. Therefore we have $\frac{|\mathsf{P}_{\psi_2} (\psi_1)|^2}{|\psi_1|^2}=\frac{|\mathsf{P}_{\psi_1} (\psi_2)|^2}{|\psi_2|^2}$. Lastly, if we take the projection of $\psi_1$ along $\psi_2$ and we project it again on $\psi_1$, we end up with a part of $\psi_1$. As this is a proper part of $\psi_1$, its state is just $\psi_1$ rescaled, no change in correlation. That is: $\mathsf{P}_{\psi_1} (\mathsf{P}_{\psi_2} (\psi_1)) = a \psi_1$ with $a \in \mathbbm{R}$.

@@

	We claim $\forall \psi \in \Psi$ there exist a projection $\mathsf{P}_\psi : \Psi \rightarrow \Psi$ with $\psi \in \Psi$. Let $\psi \in \Psi$ be a state. Let $\mathsf{P}_\psi : \Psi \rightarrow \Psi$ be an operator that returns the part of a given state that is prepared as $\psi$. $\mathsf{P}_{\psi}(c_1 \phi_1 + c_2 \phi_2) = c_1 \mathsf{P}_{\psi}(\phi_1) + c_2 \mathsf{P}_{\psi}(\phi_2)$ is linear as the part of the composition prepared like $\psi$ is the composition of the parts so prepared. $\mathsf{P}_\psi \circ \mathsf{P}_\psi = \mathsf{P}_\psi$ is a projection because the whole $\mathsf{P}_\psi$  is prepared as $\psi$.

@@

	We claim $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi)) = r \psi$ for some $r \in \mathbbm{R}$. Let $\psi, \phi \in \Psi$. Consider $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi))$: we first take the part of $\psi$ prepared like $\phi$ and then take the part of that prepared like $\psi$. The overall operation is simply returning a part of $\psi$. These must correspond to the same exact configuration for the fragments. The only thing that can change is the amount of material. Therefore $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi)) = r \psi$ for some $r \in \mathbbm{R}^+$.

@@

Also note that the observations made after \ref{prop:differentiable_manifold} for the  classical case are still valid. $\Psi$ cannot be a complete metric space as it does not include discontinuous functions. Therefore it is only a pre-Hilbert space. For mathematical convenience, one can take its completion with respect to the norm induced by the inner product and obtain a Hilbert space. Yet, such object does no longer represent a physically meaningful entity.

@@

The proceed in the following way. Suppose we have a state variable $f : \mathcal{Q} \rightarrow \mathbbm{R}$. Consider the product $f (q) \psi (q)$: it returns the value of $f$ weighted by the wave function. We can think of $f$ as an operator that takes a complex function of $\mathcal{Q}$ and returns another complex function of $\mathcal{Q}$. The operator is linear since $f (q) (a\psi_1 + b\psi_2) = a f \psi_1 + b f  \psi_2$. The operator is hermitian since $f^\dagger = f$. Consider $\langle \psi | F \psi \rangle = \langle F \psi | \psi \rangle = \int_\mathcal{Q} \psi^\dagger (q) f(q) \psi(q) dq = f(q) | \psi(q)|^2$. It integrates the value of $f$ weighted by the amount of the material: it is the expectation of the state variable $f$ over the distribution.

While $\mathcal{Q}$ is enough to define the system of units, it cannot be enough to define all the variables over which we can define the distributions. The conjugate variables $p_i=\hbar k_i$ cannot be expressed as a function of $q^i$, which reiterates the idea that we cannot specify all variables for each fragment. Suppose there is another set of state variables that provide another way to subdivide the fragments. Then those variables will form a manifold $\hat{\mathcal{Q}}$ such that each $\psi$ can be expressed as a wave function $\psi(\hat{q})$ over $\hat{\mathcal{Q}}$.

As each state $\psi$ can be identified by a wavefunction on either space, there must be an operator $\Upsilon^q_{\hat{q}}(\psi(q)) = \psi(\hat{q})$ that converts the wave function on one space to the other. As to a linear combination of states corresponds a linear combination of wave function, $\Upsilon^q_{\hat{q}}$ is a linear operator. As converting the space again must give us the original wave function, $\Upsilon^{\hat{q}}_{q} \Upsilon^q_{\hat{q}}= 1$ is unitary. We can now define a have linear operator $\hat{F}$ corresponding to state variable $\hat{f} : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$. Using $\Upsilon^{\hat{q}}_{q}$ we can express $\hat{F}$ as an operator over complex functions of $\mathcal{Q}$ It will be still be linear and hermitian.

@@

That is: for each state variable we have a corresponding linear hermitian operator which can be expressed as function multiplication in a suitable choice of $\hat{\mathcal{Q}}$.

>>>>

	We claim $\bar{\mathcal{S}}$ is the level set for $\mathcal{H} = 0$. $\mathcal{H} = \lambda (H - E) = 0$ over $\bar{\mathcal{S}}$. We can extend $\mathcal{H}$ over $T^* \mathcal{M}$ such that $\mathcal{H} \neq 0$ over $T^*\mathcal{M} \,\backslash\, \bar{\mathcal{S}}$. $\bar{\mathcal{S}}$ is the level set for $\mathcal{H} = 0$.
\end{justification}

@@

	We claim the set of physically distinguishable transformations $T$ that change the unstated part of an irreducible material is isomorphic to $\mathbbm{C}$. Consider an amount $a_m \in \mathbbm{R}$ of irreducible material characterized by one d.o.f. The configuration of a fragment of the material is characterized by two random variables $A, B: \Omega \rightarrow \mathbbm{R}$ where $\Omega$ is the sample space for the configuration of the fragments. As the configuration of each fragment is physically indistinguishable, $A$ and $B$ can be chosen such that the distribution $\rho$ of material over such variables is uniform and unitary. We can also rescale $A$ and $B$ such that they are defined on the range $[0, \sqrt{a_m}]$. We have $a_m=\int_{\Omega} \rho dA \wedge dB = \int_{\Omega} dA \wedge dB$. Consider a second amount $\hat{a}_m$ of irreducible material in the same configuration. It also can be characterized by a uniform distribution over two variables $C, D: \Omega \rightarrow \mathbbm{R}$ over a range of $\sqrt{\hat{a}_m}$. As the two amounts of material are in the same configuration, $(C,D)$ is a function of $(A,B)$. We have $\hat{a}_m = \int dC \wedge dD = \int |J| dA \wedge dB$ where $|J|$ is the Jacobian determinant. As both distributions are uniform, $|J|$ has to be constant. The transformation has to be linear: $C=aA + bB$ and $D=-bA + aB$. As the amount of material is the only physically distinguishable quantity and is fully specified by $a$ and $b$, no other transformation is physically relevant. Let $\tau: \mathbbm{C} \rightarrow T$ represent such a transformation parametrized by $c=a+\imath b$. $|c|^2 = (a^2 + b^2) = \hat{a}_m / a_m$ is the ratio of the two amounts of materials and is physically distinguishable. Define on $T$ an addition $+: T \times T \rightarrow T$ and a multiplication $*: T \times T \rightarrow T$ such that $\tau(a) + \tau(b) = \tau(a+b)$ and $\tau(a) * \tau(b) = \tau(a*b)$, $a,b \in \mathbbm{C}$, so that the sum and product of the transformation is equal to the sum and product of their respective factors. The phase $arg(c)$ under addition is physically distinguishable as it can affect the modulus of the result. $\tau$ is an isomorphism between $T$ and $\mathbbm{C}$ as fields. Assume now that the material is characterized by multiple independent d.o.f. The transformation on each d.o.f. is similarly defined by $c_i \in \mathbbm{C}$. As $\hat{a}_m / a_m$ is the same under all d.o.f. $|c_i|=|c_j|$. That has to always hold under addition as well, therefore $arg(c_i) = arg(c_j)$. $T\cong \mathbbm{C}$ even in the case of multiple d.o.f.

	We claim $\Psi$ is a vector space over $\mathbbm{C}$. The abelian group $\Psi$ can be extended with the operations defined by $T$ as was done in \ref{classical_vector space} for the infinitesimally reducible case.

@@

In the case of a reducible material, we saw how a finite amount of it was described by a distribution over the state variables of infinitesimal parts. For an irreducible material, we cannot assign states to the fragments, therefore we cannot properly talk about state variables. Therefore we call \emph{fragment variables} the quantities that we use to label the fragment configurations, and it will be over these variables that we will define the distribution of irreducible material.

Naturally, we cannot give a complete description of the configuration of the fragments, therefore we cannot give a joint distribution for all fragment variables at the same time. That is: irreducibility contains the notion of complementarity. We can, though, find a maximal set of fragment variables: one that provides the best description possible. While it should be clear that there cannot be a single unique set, we can show that one such set is provided by the fragment variables $q^i : \mathcal{Q} \rightarrow \mathbbm{R}$ that define the units required to describe the system.

In fact, we cannot add a new d.o.f. (as this would mean changing $\mathcal{Q}$) and we cannot add a new fragment variable in an existing d.o.f. (as this would fully specify said d.o.f.). Therefore the set of fragment variable $q^i$ already provide a maximal description for the fragments. This means that a state $\psi$ must tell us for each point in $\mathcal{Q}$ how much material is there and the correlation of the unstated part. That is: the state will be identified by $\psi : \mathcal{Q} \rightarrow \mathbbm{C}$, a complex function over the $\mathcal{Q}$.

The square modulus at each point will give us the density of the material. As in the classical case, such density mush be integrable to give us the total amount of material. Therefore the function $\psi(q) \in L^2(\mathcal{Q}, \mu)$ is square integrable. The norm $|\psi|^2 = \int_{\mathcal{Q}} |\psi(q)|^2 dq$ will give us the amount of material associated with the state.

As the material is homogeneous, all particles of the material are made of the same amount. We can set, by convention, the amount of material for a particle to be unitary, therefore quantum particle states are the subset of $\Psi$ such that $|\psi|^2 = 1$. As we have seen, changing the phase by a constant only affects the unstated part. Therefore unitary distributions whose differ by a total phase are not physically distinguishable and represent the same quantum particle state.

@@

	We claim $\Psi \cong \Psi(\mathcal{Q}, dp^i) \subseteq C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$ as a vector space. The maximal physical description of a set of fragments is given by a point in $\mathcal{Q}$ parametrized by $q^i$ and by a transformation in $T$ parametrized by $c \in \mathbbm{C}$. For each $\psi \in \Psi$ there must exist a wave function $\psi(q^i) : \mathcal{Q} \rightarrow \mathbbm{C}$ that provides the maximal physical description for the fragments. $\rho_\psi(q^i) = |\psi(q^i)|^2$ as the modulus of $\psi(q^i)$ is the increase/decrease from the unit amount of material. $\rho_\psi(q^i) \in C(\mathcal{Q}, \mathbbm{R})$ by \ref{continuous_map}. Therefore $\psi(q^i) \in C(\mathcal{Q}, \mathbbm{R})$. $\rho_\psi(q^i) \in L^1(\mathcal{Q}, \mu, \mathbbm{R})$ by the same arguments in the justification for \ref{integration}. Therefore $\psi(q^i) \in L^2(\mathcal{Q}, \mu, \mathbbm{C})$. Let $\Upsilon_{q^i} : \Psi \rightarrow C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$ be the function that given a state returns its wave function. As the wave function captures the maximal description of the system, two states must represent different distributions. $\forall \psi_1, \psi_2 \in \Psi, \psi_1 \neq \psi_2 \implies \Upsilon_{q^i}(\psi_1) \neq \Upsilon_{q^i}(\psi_2)$. $\Upsilon_{q^i}$ is injective. $\Upsilon_{q^i}$ is a bijection between $\Psi$ and $\Psi(\mathcal{Q}, dp^i)\equiv\Upsilon_{q^i}(\Psi)$. Let $\psi=\psi_1+\psi_2$, then $\Upsilon_{q^i}(\psi)=\Upsilon_{q^i}(\psi_1)+\Upsilon_{q^i}(\psi_2)$ as combining the distributions means combining the statistical description of the fragments. Let $\psi_1=\tau(c)\psi_2$, then $\Upsilon_{q^i}(\psi_1)=c \Upsilon_{q^i}(\psi_2)$ as $\tau(c)$ transforms the fragment configuration by the factor $C$. $\Upsilon_{q^i}$ is a homomorphism as a vector space. $\Psi$ is isomorphic to $\Psi(\mathcal{Q}, dp^i) \subseteq C(\mathcal{Q}, \mathbbm{C}) \cap L^2(\mathcal{Q}, \mu, \mathbbm{C})$.

	We claim the state space for a quantum particle is isomorphic to the projective space $\mathsf{P}(\Psi)$. Let $\psi \in \Psi$ be the state of a quantum particle. $\tau(e^{\imath \theta}) \psi$ with $\theta \in \mathbbm{R}$ is not physically distinguishable from $\psi$ as phases are only physically distinguishable through addition. $\tau(\sqrt{\rho}) \psi$ with $\sqrt{\rho} \in \mathbbm{R}^+$ cannot represent a quantum particle as it as a different amount of material. There exists only one distinguishable quantum particle state in the equivalence class $\psi \sim \tau(c) \psi$ with $c \in \mathbbm{C}$. The state with no amount of material does not correspond to any particle state. The quotient space $\mathsf{P}(\Psi) \equiv (\Psi - \{0\}) / \sim$ is isomorphic to the state of quantum particles.
\end{justification}

@@

In both the reducible and irreducible case, the material is distributed over $\mathcal{Q}$. The $q^i$ do not label the states of the material itself, but the configurations for the infinitesimal parts. For a classical material, the infinitesimal parts can be given a state, have their own topological space and a set of local state variables $(q^i, p_i)$ to identify them. We can use the richness of theory of differentiable manifolds and metric spaces. For an irreducible material, the infinitesimal parts cannot be given a state, cannot be identified by a set of local variables. We have to use other mathematical tools, such as vector spaces. As we will often use linear combination of states and we will write, for brevity, $c\psi$ instead of $\tau(c)\psi$. That is: each complex numbers still represents a state transformation.

For the tool set to be on par with classical mechanics we need to address three problems. We need to be able to compare two states and ask what fraction of them share the same configuration: this will give us an inner product. We need to be able to express distributions and expectations for different quantities: this will give us linear operators. We need to identify the conjugate quantities $k_i$ and $p_i$. Let's start with the first.

The idea is that, given two states $\psi_1$ and $\psi_2$, we should be able to tell how much of $\psi_1$ is prepared in the same way of $\psi_2$. That is $\psi_1 = \alpha \psi_2 + \psi_3$ is the combination of the component that is prepared like $\psi_2$ (e.g. same distributions in position and momentum) and a component that is prepared completely differently. Let $\mathsf{P}_{\psi_2} : \Psi \rightarrow \Psi$ be the operator that gives us the equally prepared component $\mathsf{P}_{\psi_2} (\psi_1) \equiv \alpha \psi_2$. This operator must be linear in $\psi_1$: combining components that are equally prepared still gives us components that are equally prepared. It also gives us the same result if applied once or twice: the component that is equally prepared is already fully equally prepared. $\mathsf{P}_{\psi_2}$ is therefore a projection: a linear operator such that $\mathsf{P}^2_{\psi_2}= \mathsf{P}_{\psi_2}$.

This projection has other useful properties. If $\psi_1$ is already prepared like $\psi_2$, then its projection on $\psi_2$ will be equal to $\psi_1$. Conversely, if the projection of $\psi_1$ is equal to itself, then it means that the state is already prepared like $\psi_2$. That is: $\mathsf{P}_{\psi_2} (\psi_1) = \psi_1 \Leftrightarrow \psi_1 = \alpha \psi_2$. Moreover, because the material is irreducible, if some fraction of $\psi_1$ is prepared like $\psi_2$, then the same fraction of $\psi_2$ is prepared like $\psi_1$. If not, we could learn more (or less) about $\psi_1$ by studying the component of $\psi_2$ that is prepared like $\psi_1$. Therefore we have $\frac{|\mathsf{P}_{\psi_2} (\psi_1)|^2}{|\psi_1|^2}=\frac{|\mathsf{P}_{\psi_1} (\psi_2)|^2}{|\psi_2|^2}$. Lastly, if we take the projection of $\psi_1$ along $\psi_2$ and we project it again on $\psi_1$, we end up with a component of $\psi_1$. As this is a part of $\psi_1$ prepared as $\psi_1$, its state is just $\psi_1$ rescaled, with no change in correlation. That is: $\mathsf{P}_{\psi_1} (\mathsf{P}_{\psi_2} (\psi_1)) = a \psi_1$ with $a \in \mathbbm{R}$.

@@

	We claim $\forall \psi \in \Psi$ there exist a projection $\mathsf{P}_\psi : \Psi \rightarrow \Psi$ with $\psi \in \Psi$. Let $\psi \in \Psi$ be a state. Let $\mathsf{P}_\psi : \Psi \rightarrow \Psi$ be an operator that returns the component of a given state that is prepared as $\psi$. $\mathsf{P}_{\psi}(c_1 \phi_1 + c_2 \phi_2) = c_1 \mathsf{P}_{\psi}(\phi_1) + c_2 \mathsf{P}_{\psi}(\phi_2)$ is linear as the component of the composition prepared like $\psi$ is the composition of the components so prepared. $\mathsf{P}_\psi \circ \mathsf{P}_\psi = \mathsf{P}_\psi$ is a projection because the result of $\mathsf{P}_\psi$  is prepared as $\psi$.

@@

	We claim $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi)) = r \psi$ for some $r \in \mathbbm{R}$. Let $\psi, \phi \in \Psi$. Consider $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi))$: we first take the component of $\psi$ prepared like $\phi$ and then take the component of that prepared like $\psi$. The overall operation is simply returning a part of $\psi$. These must correspond to the same exact configuration for the fragments. The only thing that can change is the amount of material. Therefore $\mathsf{P}_{\psi} (\mathsf{P}_{\phi} (\psi)) = r \psi$ for some $r \in \mathbbm{R}^+$.

@@

Also note that the observations made after \ref{prop:differentiable_manifold} for the  classical case are still valid. $\Psi$ cannot be a complete metric space (for the norm induced by the inner product) as it does not include discontinuous functions. Therefore it is only a pre-Hilbert space. For mathematical convenience, one can take its completion with respect to the norm induced by the inner product and obtain a Hilbert space. Yet, such object does no longer represent a physically meaningful set of states.

@@

We proceed in the following way. Suppose we have a fragment variable $f : \mathcal{Q} \rightarrow \mathbbm{R}$. Consider the product $f (q) \psi (q)$: it returns the value of $f$ weighted by the wave function. We can think of $f$ as an operator that takes a complex function of $\mathcal{Q}$ and returns another complex function of $\mathcal{Q}$. The operator is linear since $f (q) (a\psi_1 + b\psi_2) = a f \psi_1 + b f  \psi_2$. The operator is hermitian since $f^\dagger = f$. Consider $\langle \psi | F \psi \rangle = \langle F \psi | \psi \rangle = \int_\mathcal{Q} \psi^\dagger (q) f(q) \psi(q) dq = f(q) | \psi(q)|^2$. It integrates the value of $f$ weighted by the amount of the material: it is the expectation of the state variable $f$ over the distribution.

While $\mathcal{Q}$ is enough to define the system of units, it cannot be enough to define all the variables over which we can define the distributions. The conjugate variables $p_i=\hbar k_i$ cannot be expressed as a function of $q^i$, which reiterates the idea that we cannot specify all variables for each fragment. Suppose there is another set of state variables that provide another maximal description for the fragments. Then those variables will form a topological space $\hat{\mathcal{Q}}$ such that each $\psi$ can be expressed as a wave function $\psi(\hat{q}) :\hat{\mathcal{Q}} \rightarrow \mathbbm{C}$ over $\hat{\mathcal{Q}}$.

As each state $\psi$ can be identified by a wave function on either space, there must be an operator $\Upsilon^q_{\hat{q}}(\psi(q)) = \psi(\hat{q})$ that converts the wave function on one space to the other. As to a linear combination of states corresponds a linear combination of wave functions, $\Upsilon^q_{\hat{q}}$ is a linear operator. As converting the space again must give us the original wave function, $\Upsilon^{\hat{q}}_{q} \Upsilon^q_{\hat{q}}= 1$ is unitary. We can now define a have linear operator $\hat{F}$ corresponding to state variable $\hat{f} : \hat{\mathcal{Q}} \rightarrow \mathbbm{R}$. Using $\Upsilon^{\hat{q}}_{q}$ we can express $\hat{F}$ as an operator over complex functions of $\mathcal{Q}$. It will be still be linear and hermitian.

@@

That is: for each state variable $f$ we have a corresponding linear hermitian operator $F$ which can be expressed as function multiplication in a suitable choice of $\hat{\mathcal{Q}}$ and whose expectations is given by $\langle \psi | F \psi \rangle$.
